A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-06-17 paper/poster.tex
add another plot to poster
fancy figures for poster
brighten paper colors

\definecolor{lightyellow}{cmyk}{0,0,0.3,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=yes,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighteryellow,
  bgColorTwo=lightestyellow,
  borderColor=reddishyellow,
  headerColorOne=yellow,
  headerColorTwo=reddishyellow,
  headerFontColor=black,
  boxColorOne=lightyellow,
  boxColorTwo=lighteryellow,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  { % No eye catcher for this poster. If an eye catcher is present,
    % the title is centered between eye-catcher and logo.
    \includegraphics[height=5.5em]{figs/cavitysize-060}
  }
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  A Classical Density Functional for Water}
  % Authors
  {\sf %Sans Serif
  % Serif
  David Roundy\hspace{3em}
  Jessica Hughes\hspace{3em}
  Oregon State University, USA
  }
  % University logo
  {
    \includegraphics[height=5.5em]{figs/osu-logo}
  }

@@

  \headerbox{Surface Tension}{name=1D,column=1,row=0}{

  }
  \headerbox{A Cylinder in Water}{name=rod,column=1,below=1D,span=1,above=bottom}{
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/density-vs-radius}
    \end{center}
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/energy-vs-diameter}
    \end{center}
  }
  \headerbox{Two Cylinders in Water}{name=two rods,column=2,span=2,row=0}{
    \begin{multicols}{2}
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
    \end{multicols}\vspace{-1em}
    \begin{center}
      \includegraphics[width=0.45\columnwidth]{figs/density-rods-in-water}
      \hspace{1em}
      \includegraphics[width=0.45\columnwidth]{figs/density-rods-in-water}
    \end{center}

    %      \begin{multicols}{2}
    {
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      %Note the different scales for the two graphs.
      %Our approach has a high accuracy on the neutral (UND) dataset.
    }
    %      \end{multicols}\vspace{-1em}
  }%
  \headerbox{Future Work}{name=future work,column=2,span=1,above=bottom,below=two rods}{

>>>>

\definecolor{lightyellow}{cmyk}{0,0,0.3,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}

\definecolor{lightblue}{rgb}{0.8,0.8,1}
\definecolor{lighterblue}{rgb}{0.9,0.9,1}
\definecolor{lightestblue}{rgb}{0.98,0.98,1}

\definecolor{cyan}{cmyk}{0.4,0,0.3,0}
\definecolor{greenblue}{rgb}{0.7,1,.7}
\definecolor{mediumblue}{rgb}{0.7,0.7,1}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lightyellow,
  bgColorTwo=lightestyellow,
  borderColor=mediumblue,
  headerColorOne=lighterblue,
  headerColorTwo=mediumblue,
  headerFontColor=black,
  boxColorOne=lighterblue,
  boxColorTwo=lightblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=shade-tb,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=shade-tb,
  linewidth=2pt
  }
  % Eye Catcher
  { % The title is centered between eye-catcher and logo.
    \includegraphics[height=5.5em]{figs/cavitysize-060}
  }
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  A Classical Density Functional for Water}
  % Authors
  {\sf %Sans Serif
  % Serif
  David Roundy\hspace{3em}
  Jessica Hughes\hspace{3em}
  Oregon State University, USA
  }
  % University logo
  {
    \includegraphics[height=5.5em]{figs/osu-logo}
  }

@@

  \headerbox{Surface Tension}{name=1D,column=1,row=0}{
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/surface-tension}
    \end{center}
  }
  \headerbox{A Cylinder in Water}{name=rod,column=1,below=1D,span=1,above=bottom}{
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/density-vs-radius}
    \end{center}
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/energy-vs-diameter}
    \end{center}
  }
  \headerbox{Two Cylinders in Water}{name=two rods,column=2,span=2,row=0}{
    \begin{multicols}{2}
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
    \end{multicols}\vspace{-1em}
    \begin{center}
      \includegraphics[width=0.45\columnwidth]{figs/density-rods-in-water}
      \hspace{1em}
      \includegraphics[width=0.45\columnwidth]{figs/xassoc-rods-in-water}
    \end{center}

    %      \begin{multicols}{2}
    {
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      This text will span the whole box.
      %Note the different scales for the two graphs.
      %Our approach has a high accuracy on the neutral (UND) dataset.
    }
    %      \end{multicols}\vspace{-1em}
    \begin{center}
      \includegraphics[width=0.45\columnwidth]{figs/rods-energy-vs-distance}
    \end{center}
  }%
  \headerbox{Future Work}{name=future work,column=2,span=1,above=bottom,below=two rods}{
